%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Missions}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  \cventry
    {Product Manager - VP} % Job title
    {FWD} % Organization
    {Bangkok - Thailand} % Location
    {Oct. 2020 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Meet business goals : Products and solutions must meet the economic business goals established by the portfolio.}
        \item {Continuous Exploration to continually understand customer and market needs (Using Design thinking tools, ranging from personas, journey maps, and story maps).}
        \item {Primary responsible for building, editing, and maintaining the team backlog.}
        \item {Coordination of dependencies with other POs. During the iteration planning events.}
        \item {Communicates story detail, priorities and ensures the team aligns and agrees on a final iteration plan.}
        \item {Apply Behavior Driven Development (BDD) by collaborating with the team to detail stories with acceptance criteria.}
        \item {---}
        \item {Achievement : Thailand's 1st end-to-end fully automated digital sales process.}
      \end{cvitems}
    }
    {
      \#Enablers ~
      \#SAFe ~
      \#Solution Train Engineer (STE) ~
      \#Release on Demand ~
      \#Program Backlog ~
      \#Continuous Exploration ~
    }

%---------------------------------------------------------
  \cventry
    {Product Manager / RTE - VP} % Job title
    {SCB Life} % Organization
    {Bangkok - Thailand} % Location
    {March 2019 - Oct. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Improve the flow of value through value streams by improving and assessing the practices associated with DevOps and Release on Demand in the Continuous Delivery Pipeline.}
        \item {Assist tracking the execution of features and capabilities.}
        \item {Work with Product and Solution Management, Product Owners, and other stakeholders to help ensure strategy and execution alignment.}
        \item {Drive relentless improvement via Inspect and Adapt workshops.}
        \item {Provide input on resourcing to address critical bottlenecks.}
        \item {Assist with economic decision-making by facilitating feature and capability estimation by teams and the roll-up to Epics, where necessary.}
        \item {Help manage risks and dependencies.}
        \item {---}
        \item {Achievement: SCBLife mobile app, a one-stop shop for managing your insurance and accessing information right from your cell phone}
      \end{cvitems}
    }
    {
      \#Agile Release Train ~
      \#transformation ~
      \#Continuous Integration ~
      \#Continuous Delivery ~
    }

%---------------------------------------------------------
  \cventry
    {Product Owner - VP} % Job title
    {Krungthai-Axa} % Organization
    {Bangkok - Thailand} % Location
    {Jan. 2017 - Feb. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Ensure that the team always has an adequate amount of prior prepared tasks to work on.}
        \item {Plan and prioritize product feature backlog and development for the product.}
        \item {Define product vision, road-map and growth opportunities.}
        \item {Provide backlog management, iteration planning, and elaboration of the user stories.}
        \item {Provide an active role in mitigating impediments impacting successful team completion of Release/Sprint Goals.}
        \item {Lead the planning product release plans and set the expectation for delivery of new functionalities.}
        \item {---}
        \item {Achievements: MyAxa mobile app, new digital sales process.}
      \end{cvitems}
    }
    {
      \#Agile ~
      \#Lean ~
      \#Release plan ~
      \#Scrum ~
      \#Sprint ~
      \#Backlog ~
      \#Burndown chart ~
      \#Velocity ~
    }

%---------------------------------------------------------
  \cventry
    {Senior Consultant} % Job title
    {Palo-IT} % Organization
    {Singapore \& Bangkok - Thailand} % Location
    {March. 2013 - Dec. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Define and manage the Agile transformation program.}
        \item {Embed Agile methodology and principles in the enterprise, reflected in mindset and culture changes.}
        \item {Responsible for the direct oversight and coordination of the multiyear Agile transformation portfolio.}
        \item {Define scope, timelines, value proposition for delivery planning of projects.}
        \item {Assessing the Scrum maturity of the team and organisation and coaching the team to higher levels of maturity.}
        \item {Guiding, coaching and motivating the team with the goal of continuous improvement.}
        \item {Ensuring cross-team coordination.}
        \item {Facilitating Scrum events (Sprint Planning, Sprint Reviews and Retrospectives).}
        \item {Facilitating discussion, decision making, and conflict resolution.}
      \end{cvitems}
    }
    {
      \#Change management ~
      \#Coaching ~
      \#Consultant ~
      \#Culture ~
      \#Engagement ~
      \#Ethics ~
      \#Facilitating ~
      \#Leadership ~
      \#Process ~
      \#Product
    }

%---------------------------------------------------------
  \cventry
    {PMO - Palo IT consulting assignment} % Job title
    {Solocal Group - PagesJaunes Group} % Organization
    {Paris - France} % Location
    {Sept. 2014 - March. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Create long- and short-term plans, including setting targets for milestones, adhering to deadlines and allocating resources.}
        \item {Identify and manage potential risks and liabilities of multiple projects.}
        \item {Assist in the definition of project scope and goals.}
        \item {Communicate with executives or the board to keep the project aligned with their goals.}
        \item {Perform quality control on the project throughout development to maintain the standards expected.}
        \item {Adjust schedules and targets on the project as needed.}
        \item {Motivate people involved in the project to complete tasks on time.}
        \item {---}
        \item {Achievements: Yellow Pages mobile app, 11 million active users}
      \end{cvitems}
    }
    {
      \#Agile ~
      \#Change management ~
      \#Collaboration ~
      \#Communications ~
      \#Deliverable ~
      \#RealTime Monitoring ~
    }

%---------------------------------------------------------
  \cventry
    {PMO - Palo IT consulting assignment} % Job title
    {Carrefour} % Organization
    {Paris - France} % Location
    {Feb. 2013 - Aug. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Manage changes in project scope, schedule and costs with the help of appropriate verification techniques.}
        \item {Build and maintain relationships with third parties/vendors.}
        \item {Lead, guide and influence stakeholders regarding Project Governance and good project practices.}
        \item {Prepare and review comprehensive project documentation.}
        \item {Prepare reports and present them to senior management as needed.}
        \item {---}
        \item {Achievements: drive-thru grocery website (turnover : 630 million €).}
      \end{cvitems}
    }
    {
      \#Portfolio Management ~
      \#Steering Committee ~
      \#Component
      \#Capacity
      \#Release ~
      \#Remote ~
      \#Change control ~
    }

%---------------------------------------------------------
  \cventry
    {Mobile Application Project Manager} % Job title
    {E.Leclerc} % Organization
    {Paris - France} % Location
    {Oct. 2008 - Jan. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Acting as the point of contact for day-to-day management of assigned business and IT project.}
        \item {Collaborating with business analysts and business users to understand the business processes.}
        \item {Adhere and utilize Project Management delivery governance structure and processes.}
        \item {Monitor suppliers and subcontractors' progress and adherence to the delivery expectations.}
        \item {---}
        \item {Achievements: France's 1st price comparison mobile app.}
      \end{cvitems}
    }
    {
      \#Agile ~
      \#Native ~
      \#IOS ~
      \#Android ~
      \#AppStore ~
      \#Users ~
      \#Design ~
      \#Analytics ~
    }

%---------------------------------------------------------
  \cventry
    {Digital Project Manager} % Job title
    {Leroy Merlin} % Organization
    {Paris - France} % Location
    {Sept. 2006 - Jul. 2008} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Integrate deployment activities from each project work plan team to clearly capture key deployment milestones and dependencies.}
        \item {Develop and monitor ROI and KPIs.}
        \item {Liaise with Marketing, Sales and Product development teams.}
        \item {Regularly track and get insights into competitors' strategies.}
      \end{cvitems}
    }
    {
      \#Stakeholder ~
      \#Distribution ~
      \#Life Cycle ~
      \#Agile ~
      \#scrum ~
    }

%---------------------------------------------------------
\end{cventries}
